\documentclass[10pt]{article}
\usepackage[margin=.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fix-cm}
\raggedright
\pagestyle{empty}

%  \renewcommand{\encodingdefault}{cg}
  %\renewcommand{\rmdefault}{lgrcmr}

% DEFINITIONS FOR RESUME
\newcommand{\area}[2]{\vspace*{-9pt} \begin{verse}\textbf{#1}: #2 \end{verse}  }
\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-18pt} \hrulefill \\}
\newcommand{\header}[1]{{\hspace*{-15pt}\vspace*{6pt} \textsc{#1}} \vspace*{-6pt} \lineunder}
\newcommand{\employer}[4]{{ \textbf{#1 $\circ$ }#2 \hspace{\stretch{1}} #3 \\  \parbox{.85\textwidth}{#4}}}
\newcommand{\contact}[3]{
\begin{center}
{\LARGE \scshape {#1}}\\
#2 \lineunder 
#3
\end{center}
\vspace*{-8pt}
}
\newenvironment{achievements}{\begin{list}{$\cdot$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}\end{list}}
\newcommand{\schoolwithcourses}[4]{
 \textbf{#1} #2 $\circ$ #3 $\circ$ #4 \\ 
Selected Coursework:\\
\vspace*{5pt}
}
\newcommand{\school}[3]{
 \textbf{#1} #2 $\circ$ #3\\
\vspace*{5pt}
}
% END RESUME DEFINITIONS

\begin{document}

\contact{Matt Ball}
{376 Wickenden Street, Providence RI 02903}
{(215) 518-0870 $\circ$ mattjball@gmail}

\header{Education}

\schoolwithcourses{Brown University}{Providence, RI}{Physics Concentrator}{Projected Graduation: May 2009}
	\area{Computer Science}{Models of Computation $\cdot$ Computer Systems $\cdot$ Software Engineering $\cdot$ Networking}
	\area{Physics}{Classical Mechanics $\cdot$ Quantum Mechanics $\cdot$ Electrodynamics $\cdot$ Thermodynamics $\cdot$ Cosmology}
	\area{Mathematics}{Multivariable Calculus $\cdot$ Linear Algebra $\cdot$ Cryptography $\cdot$ Probability $\cdot$ ODEs \& PDEs}

\school{Abington Friends School}{Abington, PA}{Class of 2005}
	\area{Cumulative GPA}{4.0/4.0}
	\area{Honors}{National Cum Laude Society $\cdot$ Advanced Placement Scholar with Honor $\cdot$ Award for Outstanding Research in Human Health $\cdot$ First Place, Montgomery County Science Research Competition}

\header{Relevant Experience}
\employer{Lapis Software Associates}{Software Development Intern}{Summer 2008}{
	\begin{achievements}
	\item Developed front-end and back-end code for a web-based public health survey system.
	\item Created dynamically generated servlet-based web pages for administrator and user interaction.
	\item Implemented web server software in Java, which interacted with JSP and MySQL.
	\end{achievements}
}

\employer{Centocor, Inc.}{Summer Intern}{Summer 2006}{
	\begin{achievements}
	\item Interned with the Direct Product Capture Business Unit.
	\item Executed daily batch record reviews as part of QA and Good Manufacturing Practice.
	\item Developed a complete process map as part of a long-term project to simplify data flow.
	\item Analyzed equipment usage data to determine efficiency and forecast future needs.
	\end{achievements}
}

\header{Skills \& Interests}

\begin{achievements}
\item Proficiency in software development in Java, Python, JavaScript, C.
\item Familiarity with standard productivity and creative software, primarily Office and Adobe Creative Suite.
\item Proficiency with technical software: Crystal Reports, Mathematica, {\sc Matlab}, Kaleidagraph, Minitab.
\item Familiarity with UNIX, GNU/Linux, Windows, Macintosh operating systems.
\item Familiarity with MySQL, JSP, \LaTeX, PHP, Scheme, ML, shell scripting.
\item Interests: cooking, running, technical theatre, music, squash, skiing, Ultimate Frisbee, computers \& gaming.
\end{achievements}

\header{Additional Experience}

\employer{Brown Opera Productions}{Board Member and Webmaster}{2005 - 2009}{
	\begin{achievements}
	\item Current board member of and webmaster for BOP, a solely student-run theatre group.
	\item Served as technical director for each of BOP's annual full-length operatic productions while at Brown.
	\end{achievements}
}

\employer{Brown University Physics Department}{Summer Researcher}{Summer 2007}{
	\begin{achievements}
	\item Assisted Brown professors working in experimental high-energy particle physics.
	\item Tested and assesed a new job batching system for comparing Monte Carlo methods.
	\item Developed a series of Unix programs to efficiently configure and execute batch simulations.
	\item Created templates for manipulating results in ROOT, a data analysis library developed by CERN.
	\item Searched for particles predicted by technicolor physics models using the above tools.
	\end{achievements}
}

\employer{Fox Chase Cancer Center}{Howard Hughes Student Scientist}{2003 - 2004}{
	\begin{achievements}
	\item Researched PTEN and the molecular genetics of endometrial cancer (EC).
	\item Investigated correlations between elevated estrogen levels and incidence rate of EC.
	\item Tested glycodelin as a possible promoter of the genes \emph{lacz} and PTEN.
	\item Applied novel recombineering techniques to create a genetically altered mouse model.
	\end{achievements}
}

\end{document}
